A tutorial on the model-dependent analysis of neutron and X-ray reflectometry

### 2020-07-08 refl_maths/paper.tex
add somethign about resolution functions

Here, we will briefly discuss the introduction of a simple Gaussian resolution function of given width.

>>>>

Here, we will briefly discuss the introduction of a simple Gaussian resolution function with a constant $\sfrac{\text{d}q}{q}$. 
The Gaussian function is centred on a given wavevector, $q$, and has a width of at half maximum of $\text{d}q$.
For each $q$-value in the unsmeared data, a Gaussian function is produced which is convolved with the unsmeared to produce data that includes some description of the instrumental resolution.
Typically, this convolvutional smearing is included in the reading of the experimental data. 
However, the resolution function used by a given software package may not be an accurate description of that from the instrument, therefore, we recommend discussing this with the members of instrument staff. 
More information about the resolution function can be found in the work of van Well and Fredrikze \cite{vanwell_resolution_2005} and Nelson and Dewhurst \cite{nelson_towards_2013,nelson_towards_2014}
